---
title: "Revised Telemedicine Analysis"
author: "Catherine C. Pollack"
date: "4/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bring in Libraries and Packages
```{r}
library(tidyverse)
library(data.table)
library(lubridate)
library(magrittr)
library(tidytext)
library(textstem)
library(reshape2)
library(ggsci)
library(stopwords)
library(qdapDictionaries)
library(wordcloud)
#devtools::install_github("lchiffon/wordcloud2")
library(wordcloud2)
library(ggpubr)
library(pscl)
library(sandwich)
library(glmmTMB)
library(GLMMadaptive)
```

# Bring in Data
```{r}
#dat <- fread("/Volumes/LaCie/Cancer_COVID/Data/210426_telemedicine_covid_nodups_expand_sentiment_emotion.csv")
covid <- fread("/Volumes/LaCie/Cancer_COVID/Data/210510_all_covid_nodups_expand_sentiment.csv")
```

# Drop "0" columns
```{r}
dat %<>%
  select(-`0`)

covid %<>%
  select(-`0`)
```

# Calculating total retweets (retweets and quote tweets)
```{r}
dat %<>%
  mutate(retweet_quote_total = retweet_count + quote_count)

covid %<>%
  mutate(retweet_quote_total = retweet_count + quote_count)
```

# Part 1. Tweet Prevalence per Month (Raw, Likes, and Favorites)

## Add "month, year" column
```{r}
dat %<>%
  mutate(month_only = month(created_at),
         year_only = year(created_at) - 2000,
         month_year = paste(month_only, year_only, sep = "/"),
         date = date(created_at))

dat$month_year <- factor(dat$month_year, levels = c("1/20", "2/20", "3/20", "4/20", "5/20", "6/20", "7/20", "8/20", "9/20", "10/20", "11/20", "12/20", "1/21", "2/21", "3/21", "4/21"))

covid %<>%
  mutate(month_only = month(created_at),
         year_only = year(created_at) - 2000,
         month_year = paste(month_only, year_only, sep = "/"),
         date = date(created_at))

covid$month_year <- factor(covid$month_year, levels = c("1/20", "2/20", "3/20", "4/20", "5/20", "6/20", "7/20", "8/20", "9/20", "10/20", "11/20", "12/20", "1/21", "2/21", "3/21", "4/21"))

```

# Randomly sample covid dataset to match telemedicine dataset
```{r}
View(covid %>%
  group_by(month_year) %>%
  tally(.))

dat_sample_values <- dat %>%
  group_by(month_year) %>%
  tally(.)

set.seed(110295)
covid_january <- filter(covid, month_year == "1/20")
covid_final <- covid_january[sample(nrow(covid_january), as.numeric(dat_sample_values[1, "n"])),]

for (i in 2:(nrow(dat_sample_values)-1)) {
  print(i)
  my <- as.character(as.data.frame(dat_sample_values[i, "month_year"])$month_year)
  n <- as.numeric(dat_sample_values[i, "n"])
  
  covid_loop <- filter(covid, month_year == my)
  covid_loop_final <- covid_loop[sample(nrow(covid_loop), n),]
  
  covid_final <- rbind(covid_final, covid_loop_final)
}

dat %<>%
  filter(is.na(month_year) == FALSE)

#covid <- covid[sample(nrow(covid), nrow(dat)), ]
```

## Raw Tweets over Time
```{r}
dat %>%
  group_by(date) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = date, y = count)) +
  geom_line(color = "cornflower blue",
            size = 0.75) +
  theme_classic() +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%m/%y") +
  labs(x = "Date (Month/Year)",
       y = "Count",
       title = "Frequency of Telemedicine-COVID-19 Tweets per Day: 01/01/2020 - 04/24/2021")
#setwd("/Volumes/LaCie/Cancer_COVID/Output")
#ggsave("210426_TelemedicineTweetsPerDay.tiff", width = 7.25, height = 4.51)

dat %>%
  group_by(month_year) %>%
  summarise(total_per_month = n()) %>%
  ungroup() %>%
  mutate(percent_per_month = total_per_month/sum(total_per_month) * 100) %>%
  arrange(desc(total_per_month))
```

## Favorites Over Time
```{r}
dat %>%
  group_by(date) %>%
  summarise(count = sum(like_count, na.rm = TRUE)) %>%
  ggplot(aes(x = date, y = count)) +
  geom_line(color = "darkgreen",
            size = 0.75) +
  theme_classic() +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%m/%y") +
  labs(x = "Date",
       y = "Count",
       title = "Frequency of Telemedicine-COVID-19 Likes per Day: 01/01/2020 - 04/25/2021")
#setwd("/Volumes/LaCie/Cancer_COVID/Output")
#ggsave("210426_TelemedicineLikesPerDay.tiff", width = 7.25, height = 4.51)

dat %>%
  group_by(date) %>%
  summarise(like_count = sum(like_count, na.rm = TRUE),
            total_count = n(),
            likes_per_tweet = like_count/total_count) %>%
  ggplot(aes(x = date, y = likes_per_tweet)) +
  geom_line(color = "darkgreen",
            size = 0.75) +
  theme_classic() +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%m/%y") +
  labs(x = "Date",
       y = "Count",
       title = "Frequency of Telemedicine-COVID-19 Likes per Tweet per Day: 01/01/2020 - 04/25/2021")
#setwd("/Volumes/LaCie/Cancer_COVID/Output")
#ggsave("210426_TelemedicineLikesPerTweetPerDay.tiff", width = 7.25, height = 4.51)
```

## Retweets Over Time
```{r}
dat %>%
  group_by(date) %>%
  summarise(count = sum(retweet_quote_total, na.rm = TRUE)) %>%
  ggplot(aes(x = date, y = count)) +
  geom_line(color = "darkred",
            size = 0.75) +
  theme_classic() +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%m/%y") +
  labs(x = "Date",
       y = "Count",
       title = "Frequency of Telemedicine-COVID-19 Retweets per Day: 01/01/2020 - 04/25/2021")
#setwd("/Volumes/LaCie/Cancer_COVID/Output")
#ggsave("210426_TelemedicineRetweetsPerDay.tiff", width = 7.25, height = 4.51)

dat %>%
  ggplot(aes(x = log10(retweet_quote_total), fill = month_year)) +
  #geom_histogram(color = "black") +
  geom_density() +
  facet_wrap(~month_year) + 
  theme_classic() +
  labs(x = "Retweets (Log Base 10)",
       y = "Density",
       fill = "Date (Month/Year)",
       title = "Distribution of Retweets (Log Base 10) By Month")
setwd("/Volumes/LaCie/Cancer_COVID/Output")
ggsave("210513_TelemedicineRetweetsPerMonth_Density.tiff", width = 7.25, height = 4.51)

```

## Retweets General vs. Retweets COVID
```{r}
summary(dat$retweet_quote_total)
summary(covid_final$retweet_quote_total)

wilcox.test(dat$retweet_quote_total, covid_final$retweet_quote_total) #Significantly more likes within the COVID data set compared to the 

dat$data_set <- "Telemedicine"
covid_final$data_set <- "COVID"

all_tweets <- rbind(dat, covid_final, fill = TRUE)

dat %>%
  dplyr::filter(retweet_quote_total >= 1) %>%
  group_by(month_year) %>%
  summarise(median(retweet_quote_total),
            quantile(retweet_quote_total, 0.25),
            quantile(retweet_quote_total, 0.75))

fm1 <- mixed_model(retweet_quote_total ~ month_year + data_set, 
                   random = ~ 1 | date, 
                   data = all_tweets,
                   family = zi.poisson(), 
                   zi_fixed = ~ month_year + data_set + data_set)


model <- glmmTMB(retweet_quote_total ~ as.numeric(date) + data_set + (1|date), 
                 zi=~date+data_set, 
                 data=all_tweets, 
                 family=poisson)


model <- zeroinfl(retweet_quote_total ~ month_year*data_set, 
                  data = all_tweets,
                  dist = "poisson")

cov.m1 <- vcovCL(model, type="HC0")
std.err <- sqrt(diag(cov.m1))
r.est <- cbind(Estimate= round(exp(coef(m1)), 2), 
               "Pr(>|z|)" = round(2 * pnorm(abs(coef(m1)/std.err), lower.tail=FALSE), 3),
               LL = round(exp(coef(m1) - 1.96 * std.err), 2),
               UL = round(exp(coef(m1) + 1.96 * std.err), 2))
r.est
```

## Favorites General vs. Favorites COVID
```{r}
summary(dat$like_count)
summary(covid_final$like_count)
wilcox.test(dat$like_count, covid_final$like_count) #Significantly more likes within the COVID data set compared to the 
kruskal.test(like_count ~ month_year, data = dat)
pairwise.wilcox.test(dat$like_count, dat$month_year, p.adjust.method = "BH")

dat %>%
  #dplyr::filter(retweet_quote_total >= 1) %>%
  group_by(month_year) %>%
  summarise(median(like_count),
            quantile(like_count, 0.25),
            quantile(like_count, 0.75))
```

# Part 2: Updated Sentiment Analysis

## Categorical Sentiment Classification
```{r}
dat %<>%
  mutate(sentiment_categorical = case_when(
    compound >= 0.05 ~ "Positive",
    compound <= -0.05 ~ "Negative",
    compound > -0.05 & compound < 0.05 ~ "Neutral"
  ))
```

## Create Long Sentiment Data
```{r}
dat_long_sentiment <- dat %>%
  group_by(date) %>%
  summarise(average_neg = mean(neg, na.rm = TRUE),
            average_neu = mean(neu, na.rm = TRUE),
            average_pos = mean(pos, na.rm = TRUE),
            average_compound = mean(compound, na.rm = TRUE),
            percent_neg = length(which(sentiment_categorical == "Negative"))/n() * 100,
            percent_neu = length(which(sentiment_categorical == "Neutral"))/n() * 100,
            percent_pos = length(which(sentiment_categorical == "Positive"))/n() * 100) %>%
  melt(id = "date")

dat_long_sentiment %<>%
  mutate(variable_figure = case_when(
    variable == "percent_neg" | variable == "average_neg" ~ "Negative",
    variable == "percent_neu"| variable == "average_neu" ~ "Neutral",
    variable == "percent_pos" | variable == "average_pos"~ "Positive",
    variable == "average_compound" ~ "Compound"
  ))

```

# Changes in Categorical Sentiment
```{r}
dat_long_sentiment %>%
  filter(variable == "percent_neg" | variable == "percent_neu" | variable == "percent_pos") %>%
  ggplot(aes(x = date, y = value, color = variable_figure, group = variable_figure)) +
  geom_line() +
  theme_classic() +
  scale_x_date(date_breaks = "4 month",
               date_labels = "%m/%y") +
  facet_wrap(~variable_figure) +
  theme(axis.text.x = element_text(),
        legend.position = "bottom") +
  labs(x = "Date (Month/Year)",
       y = "Percent",
       title = "Percent of Telemedicine-COVID-19 Tweets per Sentiment per Day\n01/01/2020 - 04/25/2021",
       color = "Sentiment") +
  scale_color_npg()
setwd("/Volumes/LaCie/Cancer_COVID/Output")
ggsave("210426_TelemedicineSentimentPerDay.tiff", width = 7.25, height = 4.51)

```

# Changes in Compound Sentiment
```{r}
dat_long_sentiment %>%
  filter(variable == "average_compound") %>%
  ggplot(aes(x = date, y = value, color = variable_figure, group = variable_figure)) +
  geom_line(color = "#6164ba") +
  geom_hline(yintercept = -0.05, color = "black", linetype = "dashed") +
  geom_hline(yintercept = 0.05, color = "black", linetype = "dashed") +
  theme_classic() +
  scale_x_date(date_breaks = "2 month",
               date_labels = "%m/%y") +
  labs(x = "Date (Month/Year)",
       y = "Compound Score",
       title = "Average Compound Score of Telemedicine-COVID-19 Tweets per Day\n01/01/2020 - 04/25/2021")
setwd("/Volumes/LaCie/Cancer_COVID/Output")
ggsave("210426_TelemedicineCompoundPerDay.tiff", width = 7.25, height = 4.51)
```

# Part 3: Changes in Sentiment by Likes/Retweets

## Likes
```{r}
dat %>%
  filter(like_count != 0) %>%
  ggplot(aes(x = compound, y = log10(like_count), color = month_year)) +
  geom_point() +
  geom_vline(xintercept = -0.05, color = "black", linetype = "dashed") +
  geom_vline(xintercept = 0.05, color = "black", linetype = "dashed") +
  geom_smooth(method = "lm", color = "black") +
  theme_classic() +
  facet_wrap(~month_year) +
  labs(x = "Compound Score",
       y = "Log Likes (Base 10)",
       color = "Month/Year",
       title = "Distribution of Sentiment per Likes")
setwd("/Volumes/LaCie/Cancer_COVID/Output")
ggsave("210426_TelemedicineCompoundLogLikes.tiff", width = 7.25, height = 4.51)
```

## Retweets
```{r}
dat %>%
  filter(retweet_quote_total != 0) %>%
  ggplot(aes(x = compound, y = log10(retweet_quote_total), color = month_year)) +
  geom_point() +
  geom_vline(xintercept = -0.05, color = "black", linetype = "dashed") +
  geom_vline(xintercept = 0.05, color = "black", linetype = "dashed") +
  geom_smooth(method = "lm", color = "black") +
  theme_classic() +
  facet_wrap(~month_year) +
  labs(x = "Compound Score",
       y = "Log Retweets (Base 10)",
       color = "Month/Year",
       title = "Distribution of Sentiment per Retweet")
setwd("/Volumes/LaCie/Cancer_COVID/Output")
ggsave("210426_TelemedicineCompoundLogRetweets.tiff", width = 7.25, height = 4.51)
```

# Part 4: Extracting Dates for Random Sample of COVID-19 Tweets
```{r}
dates_for_export_df <- dat %>%
  ungroup() %>%
  group_by(month_year) %>%
  summarise(count_per_month = n()) %>%
  mutate(start_date = gsub("/", "-01-20", month_year),
         start_date = str_pad(start_date, 10, side = "left", pad = "0")) %>%
  filter(is.na(month_year) == FALSE)

end_date <- seq(as.Date("2020-02-01"),length=16,by="months")-1

dates_for_export_df <- cbind(dates_for_export_df, end_date)

setwd("/Volumes/LaCie/Cancer_COVID/Data/")
write.csv(dates_for_export_df, "210509_dates_for_random_covid.csv")
```

## Count by Month Instead
```{r}
dates_for_export_month_year <- dat %>%
  group_by(month_year) %>%
  count(.) %>%
  arrange()
```

# Part 5: Bigram and Trigram Analysis
## Cleaning
```{r}
#Tokenize
dat_tokenized <- dat %>%
  unnest_tokens(word, text)

unique_tokens <- as.data.frame(unique(dat_tokenized$word))
colnames(unique_tokens) <- "token"

# Lemmatize Words
for (i in 1:nrow(unique_tokens)) {
#for (i in 1:10) {
  if (i %% 100 == 0) {
    print(i)
  }
  word <- unique_tokens[i, "token"]
  unique_tokens[i, "lemmatized_token"] <- lemmatize_words(word)
}

dat_tokenized_lem <- left_join(dat_tokenized, 
                               unique_tokens,
                               by = c("word" = "token"))
#Count words per tweet
dat_tokenized_lem %<>% 
  count(V1, word, sort = TRUE)

#Add total unique words
total_unique_words_dat <- dat_tokenized_lem %>%
  group_by(V1) %>%
  summarise(tweet_word_count = sum(n))

#Add total words per tweet
dat_tokenized_lem <- left_join(dat_tokenized_lem, total_unique_words_dat)

#Remove english and spanish stopwords 
dat_tokenized_lem %<>%
  anti_join(stop_words) 

dat_tokenized_lem %<>%
  filter(!(word %in% stopwords(language = "es")))

#Calculate TF, IDF, and TF-IDF
dat_tfidf <- dat_tokenized_lem %>%
  bind_tf_idf(word, V1, n) %>%
  arrange(tf_idf)

#Remove words that have a low IDF in the 0.05th percentile 
dat_domain_stopwords <- dat_tfidf %>%
  distinct(word, idf) %>%
  arrange(idf) %>%
  filter(idf > quantile(idf, 0.0005))

dat_tfidf %<>%
  filter(word %in% dat_domain_stopwords$word)

# Only keeps words in English
dat_english <-  dat_tfidf %>%
  filter(word %in% GradyAugmented)

# Remove self-identified stop words
self_generated_stopwords <- c("et", "al", "trump", "si", "amp", "el", "la", "patient", "mi", "des", "les", "lo", "para", "di", "del", "hoy", "de", "los", "ー", "por", "en", "ini", "gt")

dat_english %<>%
  filter(!word %in% self_generated_stopwords)

# Count word frequency
dat_english %<>%
  group_by(word) %>%
  mutate(freq_all_tweets = n())

dat_english_distinct <- dat_english %>%
  distinct(word, .keep_all = TRUE) %>%
  arrange(desc(freq_all_tweets))

#Recalculate TF-IDF with English words only
dat_english_distinct_tfidf <- dat_english %>%
  select(-tf, -idf, -tf_idf) %>%
  bind_tf_idf(word, V1, n) %>%
  distinct(word, .keep_all = TRUE) %>%
  arrange(tf_idf)
  
dat_english_tfidf <- dat_english %>%
  bind_tf_idf(word, V1, n) %>%
  arrange(tf_idf)
```

## Bigram and Trigram Analysis
```{r}
#Bigrams
dat_bigrams <- dat %>%
  ungroup() %>%
  unnest_tokens(bigram, processed_text, token = "ngrams", n = 2)

bigrams_separated <- dat_bigrams %>%
  separate(bigram, c("word1", "word2", sep = " "))

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word 
         & word1 != "http" 
         & word1 != "https" 
         & word1 != "www" 
         & word1 %in% domain_stopwords_telemedicine$word 
         & !word1 %in% self_generated_stopwords
         & !word1 %in% stopwords(language = "es") 
         & word1 %in% GradyAugmented) %>%
  filter(!word2 %in% stop_words$word 
         & word2 %in% domain_stopwords_telemedicine$word 
         & !word2 %in% self_generated_stopwords
         & !word2 %in% stopwords(language = "es") 
         & word2 %in% GradyAugmented)

bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)

bigram_united<- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigram_counts %>%
  filter(row_number() <= 10) %>%
  unite(bigram, word1, word2, sep = " ")

#Trigrams
dat_trigrams <- dat %>%
  ungroup() %>%
  unnest_tokens(trigram, processed_text, token = "ngrams", n = 3)

trigrams_separated <- dat_trigrams %>%
  separate(trigram, c("word1", "word2", "word3", sep = " "))

trigrams_filtered <- trigrams_separated %>%
  filter(!word1 %in% stop_words$word 
         & word1 != "http" 
         & word1 != "https" 
         & word1 != "www" 
         & word1 %in% domain_stopwords_telemedicine$word 
         & !word1 %in% self_generated_stopwords
         & !word1 %in% stopwords(language = "es") 
         & word1 %in% GradyAugmented) %>%
  filter(!word2 %in% stop_words$word 
         & word2 %in% domain_stopwords_telemedicine$word 
         & !word2 %in% self_generated_stopwords
         & !word2 %in% stopwords(language = "es") 
         & word2 %in% GradyAugmented) %>%
  filter(!word3 %in% stop_words$word 
         & word3 %in% domain_stopwords_telemedicine$word 
         & !word3 %in% self_generated_stopwords
         & !word3 %in% stopwords(language = "es") 
         & word3 %in% GradyAugmented)

trigram_counts <- trigrams_filtered %>%
  count(word1, word2, word3, sort = TRUE)

trigram_united<- trigrams_filtered %>%
  unite(trigram, word1, word2, word3, sep = " ")

trigram_counts %>%
  filter(row_number() <= 10) %>%
  unite(trigram, word1, word2, word3, sep = " ")
```

## Word Cloud
```{r}
set.seed(110295)
#Need to run in Console to get everything to fit
#wordcloud(words = dat_english_distinct$word, 
#          freq = dat_english_distinct$freq_all_tweets,
#          scale = c(0.5, 0.25),
#          min.freq = 1,
#          max.words=200, random.order=FALSE, 
#          rot.per=0.15, 
#          colors=brewer.pal(8, "Dark2"))

dat_wordcloud <- dat_english_distinct %>%
  select(word, freq_all_tweets)

colnames(dat_wordcloud) <- c("word", "freq")
dat_wordcloud$freq <- as.numeric(dat_wordcloud$freq)
dat_wordcloud$word <- as.character(dat_wordcloud$word)

wordcloud2(dat_wordcloud, size = 2, minRotation = -pi/2, maxRotation = -pi/2)
```

# Part 6: Author Analysis

## Authors of Most Retweeted Tweets
```{r}
author_analysis <- dat %>% 
  select(author_id, text, retweet_count) %>%
  arrange(desc(retweet_count)) %>%
  filter(row_number() <= 100) %>%
  group_by(author_id) %>%
  mutate(author_count = n()) %>%
  arrange(desc(author_count)) %>%
  distinct(author_id, .keep_all = TRUE) #74 authors of the top 100 retweeted tweets

View(author_analysis[c(6, 7, 16, 30, 32, 39, 42, 45, 47, 55:56, 60, 63, 70)])

setwd("/Volumes/LaCie/Cancer_COVID/Data/")
write.csv(author_analysis, "210430_authoranalysis.csv")
```

## Authors of Least Retweeted Tweets
```{r}
author_analysis_lowest <- dat %>% 
  select(author_id, text, retweet_count) %>%
  arrange(retweet_count) %>%
  filter(retweet_count == 0) %>%
  group_by(author_id) %>%
  mutate(author_count = n()) %>%
  arrange(desc(author_count)) %>%
  distinct(author_id, .keep_all = TRUE) %>%
  ungroup() %>%
  slice_head(n = 100)

## Randomly sample for matching
setwd("/Volumes/LaCie/Cancer_COVID/Data/")
#write.csv(author_analysis, "210430_authoranalysis.csv")
write.csv(author_analysis_lowest, "210501_authoranalysis_lowest_random.csv")

missing <- c(1, 6, 10, 15:16, 21, 23, 28:30, 35, 41, 50:51, 56, 63, 65:66, 70, 76, 79, 91:95, 98, 100)

for (i in missing) {
  print(i)
  print(as.character(author_analysis_lowest[i, "text"]))
}
```

